Tobacco Transition Module

### 2022-12-21 docsrc/documentation/notebooks/household_income.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib"
---

# Household Income

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Data

@@

## Results

@@

```{r income_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/hh_income_2018_2019.rds")
```

## References

>>>>

---
title: "Household Income"
output: html_document
bibliography: 
  #- "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  - "../../refs.bib" # useful for debugging.
---

## Household Income

Household disposable income is a well known indicator of mental well-being.

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
notebook_setwd()
```

### Methods

@@

### Data

@@

```{r, hh_income_data}
ols_histogram("data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
```

### Results

@@

```{r income_output, echo=FALSE}
options(width=120)
ols_output(hh_income_data_path <- "data/transitions/test/hh_income_2018_2019.rds"
)
```

### References

### 2022-12-21 docsrc/documentation/notebooks/neighbourhood.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Neighbourhood

@@

## Methods

@@

## Results

@@

## References

>>>>

---
title: "Neighbourhood"
output: html_document
bibliography: 
  #- "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  - "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

## Neighbourhood

@@

### Methods

@@

### Results

@@

### References

### 2022-12-21 docsrc/documentation/notebooks/tobacco.Rmd
get all current module templates with better formatting in taskbar.
bug fixing income, labour models. adding visualisation plots to all models for notebooks

# Tobacco

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Results

@@

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
```

## References

>>>>

## Tobacco

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
notebook_setwd()

```

### Methods

@@

```{r tobacco_data}
zip_density("data/transitions/test/tobacco_zip_2018_2019.rds", 'y')
```
### Results

@@

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("data/transitions/test/tobacco_zip_2018_2019.rds")
```

### References
